Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 egpaper_final.tex

We modeled the distribution of the convolution as an exponential distribution
and used Gaussian as our proposal distribution.

We run experiments on PASCAL 2007 car category images with at least one car
(num images) and got x percent improvement after fine tuning.

Suppose that $x = [p, m, f]$ where $p$ is the 3D rotation of the CAD model and
$m$ is the CAD model index and $f$ is the focal length. Then we sample $x$ using 
% there are several advantages that was not possible such as \textbf{on-the-fly} template generation and making large number of templates  
\begin{figure}[t]
\centering
    \includegraphics[width=0.7\linewidth]{tuning2} \\ [-5pt]
    \caption{Different modes of Metropolis Hasting proposals, see Section \ref{sec:fine}}
 \label{fig:tuningmode}
\end{figure}

>>>>

To fine-tune continuous pose and location of object, we require strong
initialization. The initialization is a rough bounding box with small context
and viewpoint. Since most of the standard detectors does not provide viewpoint
of an object, we first run an ensemble of NZ-WHO templates to get rough
viewpoints. Once we get rough viewpoint, we initialize the proposal $x_0$ and
start sampling proposals.

We modeled the distribution of object location and pose as an exponential distribution. 
For proposal distribution, we used Gaussian distribution to propose next viewpoint and for viewpoint proposals
and uniform distribution for model change proposals.

More formally, suppose that $x = [p, m, f]$ where $p$ is the 3D rotation of the CAD model and
$m$ is the CAD model index and $f$ is the focal length. We use Metropolis Hastings
to optimize $x$.

\begin{align}
    A(x \rightarrow x') & =  min\left( 1,  \frac{P(x' g(x') \rightarrow x)}{P(x) g(x \rightarrow x')}\right) \\
    g(x \rightarrow x + p_i') & \sim \mathcal{N}(\mu = 0,\sigma = c_1) \quad i \in \{1,2,3\}\\
    g(x \rightarrow x + f') & \sim \mathcal{N}(\mu = 0,\sigma = c_2)\\
    g(x \rightarrow x + m') & \sim c_3 \delta(m) + (1-c_3) Unif(1,M)
\end{align}

Where $g$ is the proposal distribution and $P$ is the distribution of which we
defined using Gaussian distribution around previous state. $A$ is the
acceptance probability where we accept new proposal with $A(x \rightarrow x')$.

\begin{align}
    P(x) & \sim e^{ c_4 \max_{s} w(x) \ast \mathcal{T}_s(\mathcal{I}) }
\end{align}

$P$ is the distribution of the pose and location of an object on image
$\mathcal{I}$. One can also think of the image as an image cropped by detection
bounding box. We synthesize covariance matrix and create NZ-WHO template $w(x)$ for particular viewpoint, focal length and CAD model.

We initialize the $x$ using the result from the previous stage where we run our ensemble or NZ-WHO templates to get rough estimate.

In sum, for new proposal $x'$, we make a NZ-WHO template on the fly 
We found out that it requires good initialization to converge to local minima.

We represented the probability using exponential family.

So our model favors large convolution score $\max_{s} w(x) \ast T(\mathcal{I})$.

% there are several advantages that was not possible such as \textbf{on-the-fly} template generation and making large number of templates  
\begin{figure}[t]
\centering
    \includegraphics[width=0.7\linewidth]{tuning2} \\ [-5pt]
    \caption{Different modes of Metropolis Hasting proposals, see Section \ref{sec:fine}}
 \label{fig:tuningmode}
\end{figure}
